---
title: "Hacker News Analysis"
author: "Johannes Nakayama"
date: "2021-01-09"
output: 
  prettydoc::html_pretty:
    theme: tactile
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(tidyverse)
library(magrittr)
library(ggpubr)
source("helpers.R")
```






# Analysis of Required Sampling Rate

For any analysis of Hacker News over a period of time, it is first important to know at which rate the stories need to be sampled. The following plot displays the top 10 stories from Hacker News over the period of one hour. As can be seen, The developments are not as volatile as to require a sampling rate of 2 or 4 minutes. Even with a six minute sampling rate, the developments are still depicted reasonably accurately. For the further analyses, I chose a sampling rate of 5 minutes.

```{r}

h1_data <- arrow::read_feather(file.path("..", "data", "h1_data.feather"))
eda_data <- arrow::read_feather(file.path("..", "data", "eda_data.feather"))

h1_data %<>% 
  mutate(id = as.factor(id),
         creation_time = as.POSIXct(creation_time, origin = "1970-01-01", tz = "UTC"), 
         score = as.numeric(score),
         comment_count = as.numeric(comment_count),
         timestamp = as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC"),
         rank_at_timestamp = as.ordered(rank_at_timestamp))

eda_data %<>% 
  mutate(id = as.factor(id),
         creation_time = as.POSIXct(creation_time, origin = "1970-01-01", tz = "UTC"), 
         score = as.numeric(score),
         comment_count = as.numeric(comment_count),
         timestamp = as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC"),
         rank_at_timestamp = as.ordered(rank_at_timestamp))

h1_data %>% 
  group_by(timestamp) %>% 
  summarize(timestamp = unique(timestamp)) %>%
  ungroup() %>% 
  arrange(timestamp) -> timestamp_ordering

timestamp_ordering$ts_id <- 1:dim(timestamp_ordering)[1]

h1_data %<>% inner_join(timestamp_ordering, by = "timestamp")

```




```{r, fig.height=4, fig.width=7, fig.align="center", out.width="100%", dpi=300}

plot_details <- theme_hn() +
  theme(legend.position = "None",
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank())

h1_data %>% 
  filter(rank_at_timestamp <= 10) %>% 
  ggplot(aes(x = timestamp, y = score, color = id)) +
  geom_point() +
  geom_line() +
  ggtitle("2 Minutes") +
  plot_details +
  theme(legend.position = "None",
        plot.title = element_text(margin = margin(t = 10, b = 10))) -> p1

h1_data %>% 
  filter(rank_at_timestamp <= 10) %>% 
  filter(ts_id %% 2 == 0) %>% 
  ggplot(aes(x = timestamp, y = score, color = id)) +
  geom_point() +
  geom_line() +
  ggtitle("4 Minutes") +
  plot_details +
  theme(legend.position = "None",
        plot.title = element_text(margin = margin(t = 10, b = 10))) -> p2

h1_data %>% 
  filter(rank_at_timestamp <= 10) %>% 
  filter(ts_id %% 3 == 0) %>% 
  ggplot(aes(x = timestamp, y = score, color = id)) +
  geom_point() +
  geom_line() +
  ggtitle("6 Minutes") +
  plot_details +
  theme(legend.position = "None",
        plot.title = element_text(margin = margin(t = 10, b = 10))) -> p3

ggarrange(p1, p2, p3, nrow = 1) %>% 
  annotate_figure(top = text_grob(label = "Development of Top 10 Stories for Different Sampling Rates",
                                  color = "grey20",
                                  size = 15),
                  left = text_grob(label = "Score",
                                   color = "grey20",
                                   rot = 90),
                  bottom = text_grob(label = "Timestamp",
                                     color = "grey20")) +
  theme(plot.background = element_rect(color = "grey70", fill = "grey70", size = 1),
        plot.margin = margin(15, 15, 15, 15)) +
  NULL

```



Maximum age for top stories?
All new stories in top stories?
Minimum number of votes to make the top list

-> Data to Github

Longterm:
* Stackoverflow


# Preliminary Analysis of Five Hours


```{r, fig.align="center", out.width="100%", dpi=300}

newstories <- arrow::read_feather(file.path("..", "data", "newstories.feather"))

newstories %<>%
  mutate(story_id = as.factor(story_id),
         timestamp = as.POSIXct(timestamp, origin = "1970-01-01", tz = "UTC"),
         rank = as.numeric(rank))

newstories %>% 
  filter(rank <= 50) -> newstories_toppage

n_stories <- newstories_toppage$story_id %>% unique() %>% length()

color_scheme <- rep(c("black", "white"), n_stories)

newstories_toppage %>% 
  ggplot(aes(x = timestamp, y = rank, color = story_id, alpha = 30 - rank)) +
  scale_color_manual(values = color_scheme) +
  geom_point(size = 2) +
  geom_line(size = 1) +
  scale_y_continuous(trans = "reverse", breaks = seq(50, 1, -5)) +
  theme(legend.position = "None") +
  geom_hline(yintercept = 30, linetype = "dashed", color = "red", size = 2) +
  theme_hn() +
  theme(
    panel.grid.minor.y = element_blank()
  )

ggsave("test.jpg", width=10, height=5)

```




```{r}

topstories <- arrow::read_feather(file.path("..", "data", "topstories.feather"))
topstories %<>% 
  mutate(id = as.factor(id),
         creation_time = lubridate::as_datetime(creation_time),
         score = as.numeric(score),
         comment_count = as.numeric(comment_count),
         scrape_timestamp = lubridate::as_datetime(scrape_timestamp),
         slice_timestamp = lubridate::as_datetime(slice_timestamp),
         rank_at_timestamp = as.ordered(rank_at_timestamp))

```


```{r}
# general metrics

n_stories <- topstories$id %>% unique() %>% length()
n_creators <- topstories$creator_username %>% unique() %>% length()



```

There are `r n_stories` stories by `r n_creators` different users in the data set.


```{r}

topstories %>% 
  ggplot(aes(x = creation_time)) +
  # geom_histogram() +
  geom_density(color = "white", fill = "white", alpha = 0.5, size = 2) +
  scale_x_datetime(date_breaks = "4 hours") +
  theme_hn() +
  theme(axis.text.x = element_text(angle = 90))

```



```{r}

topstories %>% 
  ggplot(aes(x = score)) +
  geom_histogram(fill = "white") +
  theme_hn()

```



Comment count (stories with more than 500 comments excluded)

```{r}
topstories %>% 
  filter(comment_count < 500) %>% 
  ggplot(aes(x = comment_count)) +
  geom_histogram(binwidth = 10, fill = "white") +
  theme_hn()
```

How do stories develop that have at some point reached rank 1?

```{r}

min_rank <- 160

topstories %>% 
  filter(rank_at_timestamp == 1) %>% 
  select(id) %>% 
  unique() -> rank_one_joiner

color_scheme <- sample(viridis::magma(dim(rank_one_joiner)[1]))

topstories %>% 
  inner_join(rank_one_joiner, by = c("id")) %>% 
  mutate(rank_at_timestamp = as.numeric(rank_at_timestamp)) %>% 
  ggplot(aes(x = slice_timestamp, y = rank_at_timestamp, color = id)) +
  geom_point(size = 0.2, alpha = 0.8) +
  geom_line(size = 0.2, alpha = 0.6) +
  scale_color_manual(values = color_scheme) +
  scale_y_continuous(trans = "reverse", limits = c(min_rank, 1)) +
  theme_hn() +
  theme(legend.position = "None") +
  NULL

ggsave("topstory_development.jpg", width = 8, height = 4)

```
































