---
title: "Hacker News Analysis"
output: 
  prettydoc::html_pretty:
    theme: tactile
---


```{r setup, include=FALSE, warning=FALSE}

# defaults and libraries
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(dplyr)
library(ggplot2)
library(magrittr)
library(tidyr)
library(gganimate)
source("helpers.R")

# load / preprocess data
if (!("hn-data-processed.rds" %in% list.files(file.path("..", "data")))) {
  source("preprocess.R")
} else {
  data <- readr::read_rds(file.path("..", "data", "hn-data-processed.rds"))  
}

```



### Arrival Rate as Poisson Process

We model the number of stories arriving per minute with a Poisson distribution. For this estimation, we limit our data set to stories that were submitted *after* we started sampling. For older stories, the exact arrival counts are not computable (you might consider this a "cold start problem").

```{r format-data-for-submission-times}

# crop the data to only include stories which were surveyed from the time of their submission
sampling_start <- min(data$samptime_datetime)
data %>% filter((subtime_datetime >= sampling_start)) -> data_subtimes_cropped

# get IDs and submission times and sort them in ascending order by submission time
data_subtimes_cropped %>% 
  select(id, subtime_datetime) %>% 
  distinct() %>% 
  arrange(subtime_datetime) %>% 
  select(subtime_datetime) -> sorted_submission_times

# compute for every 1 minute time slice how many new stories are posted
tibble(subtime = sorted_submission_times$subtime_datetime, 
       bin = cut(sorted_submission_times$subtime_datetime, 
                 breaks = "1 min", labels = FALSE)) %>% 
  mutate(bin = factor(bin, levels = seq(1, max(bin), by = 1))) %>% 
  group_by(bin, .drop = FALSE) %>% 
  summarize(arr_count = n()) -> arrival_counts

```

The Poisson distribution has one parameter, $\lambda$, which is simply the arithmetic mean. Thus, the arrival times distribution function can easily be computed as follows to simulate the process.

```{r simulate-arrival-rates}
# simulate this process
set.seed(1)
n <- dim(arrival_counts)[1]
lambda <- mean(arrival_counts$arr_count)
simulated_distribution <- tibble(simulated_arr_count = rpois(n, lambda))

arrival_counts_long <- arrival_counts %>% 
  cbind(simulated_distribution) %>% 
  tidyr::pivot_longer(cols = c(arr_count, simulated_arr_count), names_to = "type", values_to = "value")

arrival_counts_long$type %<>% factor()
levels(arrival_counts_long$type) <- list(empirical = "arr_count", simulated = "simulated_arr_count")
```




```{r}
# plot generics
y_max <- 10000
rate_max <- 7

arrival_counts_long %>% 
  ggplot(aes(x = value, fill = type)) +
  geom_bar(position = "dodge", alpha = 0.6, color = "transparent") +
  ylim(c(0, y_max)) +
  scale_x_continuous(trans = "reverse", breaks = seq(rate_max, 0, by = -1), limits = c(rate_max + 0.5, -0.5)) +
  scale_fill_manual(values = c("empirical" = "black", "simulated" = "red")) +
  labs(title = "Distribution of Arrival Rate per Minute",
       x = "Arrival Rate",
       y = "Count") +
  coord_flip() +
  theme_hn() +
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.title = element_blank())
```

Plotting the simulated arrival rates against the empirical one shows that the process is very accurately modeled with the Poisson distribution. 





```{r}


data_raw %>% 
  mutate(tick_10 = floor(tick / 10)) %>% 
  mutate(topRank = as.numeric(topRank)) %>% 
  group_by(tick_10, topRank, id) %>% 
  summarize(count = n())


sample_range <- max(data_raw$sample_time) - min(data_raw$sample_time)

# das müsste auch in der Simulation rauskommen

data_raw %>% 
  select(id, topRank) %>% 
  mutate(topRank = as.numeric(topRank)) %>%
  filter(!is.na(topRank)) %>% 
  distinct() %>% 
  group_by(topRank) %>% 
  summarize(count = n()) %>% 
  ungroup() %>% 
  mutate(count = sample_range / count) %>% 
  ggplot(aes(x = topRank, y = count)) +
  geom_point() +
  geom_line() +
  scale_y_log10()

```


```{r}

data %>% 
  mutate(rank_newpage = as.integer(rank_newpage)) %>% 
  mutate(gained_votes = as.integer(gained_votes)) %>%  
  replace_na(list(rank_toppage = 0)) %>% 
  mutate(rank_toppage = as.integer(rank_toppage)) -> data_new


data_new %>% 
  select(gained_votes, rank_toppage, score) %>% 
  # filter((rank_toppage == 0) & (gained_votes > 0)) %>%
  group_by(rank_toppage, score) %>% 
  summarize(gained_sum = sum(gained_votes, na.rm = TRUE),
            gained_mean = mean(gained_votes, na.rm = TRUE),
            gained_median = median(gained_votes, na.rm = TRUE),
            count = n(), 
            ) %>% 
  ungroup() -> data_new

# data_new %>% filter((rank_toppage == 0) & (gained != 0))

```

```{r}

data_new$jitter <- runif(dim(data_new)[1], -0.5, 0.5)

data_new %>%
  filter(gained_sum > 0) %>% 
  filter(rank_toppage > 0) %>% 
  mutate(score_jittered = score + jitter) %>% 
  mutate(gained_mean_log = log(gained_mean)) %>% 
  ggplot(aes(x = score_jittered, y = rank_toppage, color = gained_mean_log)) +
  geom_point() +
  scale_color_viridis_c() +
  scale_y_reverse() +
  scale_x_log10()


# social proof bias
# -> muss bei Simulation (Voting behavior beachtet werden)

```



```{r}
(
  data_new %>% 
    filter(rank_toppage < 60) %>% 
    filter(count > 50) %>% 
    mutate(gained_mean = log(gained_mean)) %>%
    # replace_na(list(gained = 0)) %>%
    mutate_all(function(x) ifelse(is.infinite(x), -7, x)) %>%
    ggplot(aes(x = score, y = rank_toppage, fill = gained_mean)) +
    geom_tile() +
    labs(title = "Gained votes on new vs. top page",
         x = "newpage rank",
         y = "toppage rank",
         fill = "gained votes") +
    scale_y_reverse() +
    coord_fixed() +
    scale_fill_viridis_c() +
    # scale_fill_gradient(low = "darkblue", high = "yellow") +
    # scale_fill_gradientn(colours = c("darkblue", "red", "orange",  "yellow")) +
    theme_hn() -> tile_plot
)

# ask und best etc. rausfiltern
# Plot wie sich einzelne Storys entwickeln in diesem Raster
# normalisieren

```



top rank vs. score